An Interpretable Machine Learning Framework for Modeling High-Resolution Spectroscopic Data\footnote{Open source code at \url{https://github.com/gully/blase}}

### 2022-09-26 paper/paper1/ms.tex
OK, I think I might be done with the referee comments.  Yay!

\subsection{Starspots and magnetic fields}
One current assumption of starspot spectral decomposition is that the starspot spectrum itself resembles the stellar photosphere of a cooler star.  This assumption appears adequate for detecting starspot spectra and measuring their physical properties \citep{gullysantiago17}.  But to second order starspots should exhibit some spectral peculiarities that make them depart from a ``normal'' stellar photosphere.  We may be probing deeper into the photosphere, and so the lines may experience higher pressure, with slightly different line widths.  Or maybe the finite convective velocity shift can be directly seen as systematic shifts of the spectral lines (as stated in Section \ref{eprv}).

@@

Often the most spotted stars are also rapidly rotating, and so the large $v\sin{i}$ blurs the starspot spectrum into the spot-free component of the photosphere.  One experiment could measure the starspot spectral peculiarities more easily: obtainhigh resolution spectra of a pole-on (or nearly pole-on) young star where the lines will be sharp and the two components of the spectra should be more easily discernable.

Relatedly, magnetic fields information could be incorporated into  \emph{blas\'e} as line-by-line Land\'e $g-$factors, to allow magnetic sensitive lines to exhibit either Zeeman broadening or Zeeman splitting.  This labelling could be conducted in the same way as described in Section \ref{secMissingLines}.

>>>>

\subsection{Starspots and magnetic fields}
One current assumption of starspot spectral decomposition is that the starspot spectrum itself resembles the stellar photosphere of a cooler star.  This assumption appears adequate for detecting starspot spectra and measuring their physical properties \citep{2017ApJ...836..200G}.  But to second order, starspots should exhibit some spectral peculiarities that make them depart from a ``normal'' stellar photosphere.  We may be probing deeper into the photosphere, and so the lines may experience higher pressure, with slightly different line widths \citep{oneal96}.  Or maybe the finite convective velocity shift can be directly seen as systematic shifts of the spectral lines (as stated in Section \ref{eprv}).

@@

Relatedly, magnetic field information could be incorporated into \emph{blas\'e} as line-by-line Land\'e $g-$factor ``labels'', when available. The use of the labels could take a few different forms. \edit1{The labels could simply serve as flags, to indicate that regularization should be weakened to allow these magnetic sensitive lines to wander farther from their naive non-magnetic expectations.  Or the labels could be used to infer the extent of Zeeman broadening or Zeeman splitting by parameterizing these operations as convolutions.  The best choice for how to incorporate magnetic sensitivity into the flexibility of \emph{blas\'e} remains an open research question.}
